Geometric models reveal the hidden structure of conceptual knowledge

### 2023-01-25 paper/main.tex
finished remaining methods section, added in (captionless) held-out-questions figure

@@

>>>>

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{figs/held-out-question-analyses}

    \caption{\textbf{Estimating knowledge for held-out questions.}}

    \label{fig:predictions}
\end{figure}

@@

\subsubsection*{Testing the ``smoothness'' of knowledge}

A core assumption of our modeling framework is that knowledge is ``smooth''
such that knowing about one concept implies knowledge about other related
concepts (i.e., concepts that are nearby in text embedding space). Conversely,
\textit{not} knowing about a given concept implies \textit{less} knowledge
about other related concepts. We characterized how estimated knowledge (and
lack of knowledge) fell off with distance in the text embedding space
(Fig.~\ref{fig:predictions}, top panels).

For each participant, for each quiz, for each of $c$ correctly answered
question $q$ in turn, we sorted all of the other correctly answered questions
in descending order of their topic vectors' correlations with $q$'s topic
vector. We repeated this for all correctly answered questions to obtain a $c
\times (c - 1)$ matrix of correlations, where the rows corresponded to held-out
questions and the columns corresponded to the most similar (leftmost column),
second most similar (second column), other correctly answered questions. Note
that each correlation for each pair of questions ($a$ and $b$) appears exactly
twice in this matrix: once when $a$ is the held-out question, and once when $b$
is the held-out question. We applied the Fisher $z$-transformation to these
correlations, averaged down the rows, and then applied the inverse Fisher
$z$-transformation to obtain a $1 \times (c - 1)$ array of average correlations
for the participant. We repeated this process across all $n$ participants,
yielding an $n \times 14$ matrix (15 is the maximum number of questions that
could have been answered correctly on any single 15-question quiz, so at most
14 correctly answered questions could be compared to a held-out correctly
answered question). Note that some of the entries, for some of the
participants, were empty (e.g., if a given participant answered at least one
question incorrectly, they would never have 14 other correctly answered
questions to compare to a held-out correctly answered question). If a
participant answered \textit{no} questions correctly on a given quiz, their
entire row would be empty.

The blue ribbon plots in the top panels of Figure~\ref{fig:predictions} display
the mean (across participants) and bootstrap-estimated 95\% confidence
intervals of these matrices (i.e., one per quiz, each plotted in a separate
panel). We repeated the same process for \textit{incorrectly} answered
questions (i.e., comparing held-out incorrectly answered questions to other
incorrectly answered questions from the same quiz, for each participant in
turn) to obtain the red ribbon plots in the top panels of
Figure~\ref{fig:predictions}.

If we are able to accurately estimate a participant's knowledge about the
content tested by a given question, the estimated knowledge should have some
predictive information about whether the participant is likely ot answer the
question correctly or incorrectly. For each question in turn, for each
participant, we used Equation~\ref{eqn:prop} to estimate (using all
\textit{other} questions from the same quiz, from the same participant) the
participant's knowledge at the held-out question's embedding coordinate. For
each quiz, we aggregated these estimates into two distributions: one for the
estimated knowledge at the coordinates of each \textit{correctly} answered
question, and anotehr for the estimated knowledge at the coordinates of each
\textit{incorrectly} answered question (Fig.~\ref{fig:predictions}, bottom
panels). We then used independent samples $t$-tests to compare the means of
these distributions of estimated knowledge.
